HMM Model development

### 2020-05-14 dev/hmm_model_devel.Rmd
First working version of using brms predictors

```{r}
data <- hmm_simulator(10, 20, 2, use_noisy_states = TRUE)
cc <- make_stancode_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data)

@@

all_data <- c(make_standata( make_brms_formula_hmm(data$observed_structured$formula), data = prep_data$brmsdata),
              prep_data$standata)

sampling(model2, data = all_data)

@@

test_data <- data.frame(a = c(1,2,3), b = c(0.5,1.0,1.5), x1 = c("A"), x2 = c(0,1,2))
# f <- cbind(a,b) ~ 0 + (0 + x2 | a | x1)
# make_stancode(f, data = test_data)
# make_standata(f, data = test_data)

>>>>

```{r}
data <- hmm_simulator(5, 10, 2, use_noisy_states = FALSE)
cc <- make_stancode_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data, prior= data$observed_structured$prior)

@@

all_data <- make_standata_hmm(data$observed_structured$formula, serie_data = data$observed_structured$serie_data, rate_data = data$observed_structured$rate_data, state_data = data$observed_structured$state_data)

fit_raw <- sampling(model2, data = all_data)
#TODO - compactification is necessary!
```

@@

test_data <- data.frame(a = c(1,2,3), b = c(0.5,1.0,1.5), x1 = c("A"), x2 = c(0,1,2))
f <- a ~ 0 + (0 + x2 | a | x1)
# make_stancode(f, data = test_data)
#brms::make_standata(f, data = test_data)
xx <- brms::brmsformula(f)

xx$resp
